White Dwarf Mergers on Adaptive Meshes\\ II. Collisions

### 2017-09-09 papers/wdmerger_II/paper.tex
Update description of T floor effect

We tested a few other parameters that ended up having no serious effect on the outcome.
The dual energy parameter $\eta_2$ described in \autoref{sec:problemsetup} can have a
minor effect on the nickel production, yielding variations on the order of a few percent,
but there is no clear pattern. The dual energy parameter $\eta_3$ has no effect on the
outcome: the answer is the same for $\eta_3 = 0$ and $\eta_3 = 1$, which makes sense
because all of the reacting regions have a low enough kinetic energy relative to their
total energy such that the internal energy variable is always kept in sync with $(E - K)$.
(We did not look at $\eta_1$ because that has a direct effect only on the hydrodynamics,
not the reactions.) We also tested whether our choice for the temperature floor mattered
by lowering it to $10^6\ \text{K}$ and $10^5\ \text{K}$, and this had no effect on nickel
production. It does allow parts of the WDs to become colder as they move, due to numerical
errors in the advecting flow (the Helmholtz equation of state is very insensitive to
temperature, so even small changes in the internal energy can create very large changes
in the implied temperature), but the amount of energy injected by the collision is so
large that the final result is insensitive to whatever the initial temperature of the
WDs were. We also checked whether there was any consequence of our choice to disable the
burning for small enough $\rho$ and $T$. Lowering the minimum $\rho$ for reactions to
$10^0\ \text{g cm}^{-3}$ from $10^6\ \text{g cm}^{-3}$ had a negligible effect,
and varying the minimum $T$ for reactions from $2 \times 10^{7}\ \text{K}$ to
$4 \times 10^{8}\ \text{K}$ also had no meaningful effect.

>>>>

We tested a few other parameters that ended up having no serious effect on the outcome.
The dual energy parameter $\eta_2$ described in \autoref{sec:problemsetup} can have a
minor effect on the nickel production, yielding variations on the order of a few percent,
but there is no clear pattern. The dual energy parameter $\eta_3$ has no effect on the
outcome: the answer is the same for $\eta_3 = 0$ and $\eta_3 = 1$, which makes sense
because all of the reacting regions have a low enough kinetic energy relative to their
total energy such that the internal energy variable is always kept in sync with $(E - K)$.
(We did not look at $\eta_1$ because that has a direct effect only on the hydrodynamics,
not the reactions.) We also tested whether our choice for the temperature floor mattered
by lowering it to $10^6\ \text{K}$ and $10^5\ \text{K}$; this had a minor effect on nickel
production, again on the order of a few percent. It does allow parts of the WDs to
become colder as they move, due to numerical errors in the advecting flow (the Helmholtz
equation of state is very insensitive to temperature, so even small changes in the internal
energy can create very large changes in the implied temperature), but the amount of energy
injected by the collision is so large that the final result is largely insensitive to whatever
the initial temperature of the
WDs were. We also checked whether there was any consequence of our choice to disable the
burning for small enough $\rho$ and $T$. Lowering the minimum $\rho$ for reactions to
$10^0\ \text{g cm}^{-3}$ from $10^6\ \text{g cm}^{-3}$ had a negligible effect,
and varying the minimum $T$ for reactions from $2 \times 10^{7}\ \text{K}$ to
$4 \times 10^{8}\ \text{K}$ also had no meaningful effect.
